---
output:
  html_document: default
  pdf_document: default
---


```{r}
#Installing & Loading all needed packages
# install.packages("tidyverse")
# install.packages("corrplot")
library(tidyverse)
library(ggplot2)
library(dplyr)
library(corrplot)

```

Loading dataset

Top 5 data rows

```{r}

df <- read_csv("Customer behaviour Tourism.csv")
head(df, 5)
```


Bottom 5 data rows

```{r}
tail(df, 5)
```


Checking structure of the dataset, data types of all the columns

```{r}
# checking structure of dataset
glimpse(df)
```


Checking dataset for duplicate values

```{r}
sum(duplicated(df))
```



checking dataset for null values

```{r}

null_values <- df %>% map(~sum(is.na(.)))
null_values
```

Find average or most common values from columns to replace NA with that values from each column that have NA values

```{r}

# Find average value
avg_yavotp <- round(mean(df$Yearly_avg_view_on_travel_page, na.rm = TRUE))

# Find the most common value in the 'preferred_device' column
most_common_device <- names(which.max(table(df$preferred_device)))

# Find average value of likes
avg_like_given <-  round(mean(df$total_likes_on_outstation_checkin_given, na.rm = TRUE))

# Find average yearly outstation check in
avg_check_in <-  round(mean(df$yearly_avg_Outstation_checkins, na.rm = TRUE))

# Find most column value in the 'preferred_location_type' column
most_common_location <- names(which.max(table(df$preferred_location_type)))

# Find average yearly comment on page
avg_comment <-  round(mean(df$Yearly_avg_comment_on_travel_page, na.rm = TRUE))

# Most common value in the 'following_company_page'
most_common_ans <- names(which.max(table(df$following_company_page)))

# Most common adult flag
most_common_adult_flag <- names(which.max(table(df$Adult_flag)))

# Find average of daily spending on traveling page
avg_time_spend_page <- round(mean(df$Daily_Avg_mins_spend_on_traveling_page, na.rm = TRUE))


df <- df %>% replace_na(list(Yearly_avg_view_on_travel_page = avg_yavotp, preferred_device = most_common_device, total_likes_on_outstation_checkin_given = avg_like_given, yearly_avg_Outstation_checkins = avg_check_in, preferred_location_type = most_common_location, Yearly_avg_comment_on_travel_page = avg_comment, following_company_page = most_common_ans, Adult_flag = as.integer(most_common_adult_flag), Daily_Avg_mins_spend_on_traveling_page = avg_time_spend_page))

null_values2 <- df %>% map(~sum(is.na(.)))
null_values2
```


Checking specific columns for unique values

Before fixing - unique values

```{r}


unique(df$Taken_product)

unique(df$preferred_device)

unique(df$member_in_family)

unique(df$preferred_location_type)

unique(df$following_company_page)

unique(df$working_flag)

unique(df$travelling_network_rating)

unique(df$Adult_flag)
```


Setting values from preferred device column in categories

```{r}

# Create a new column 'device_category' based on mapping

temp_preferred_device <- df %>% mutate(device_category = case_when(preferred_device %in% c('iOS and Android', 'iOS', 'ANDROID', 'Android', 'Android OS', 'Other', 'Others', 'Tab') ~ 'Mobile', TRUE ~ preferred_device))

df <- df %>%  mutate(device_category = temp_preferred_device$device_category)
```


Fixing Values from columns

```{r}

# replacing "Three" with "3" and converting whole column to numeric data type from character data type - 'member_in_family' column

temp_member_in_family <- df %>% mutate(member_in_family = ifelse(member_in_family == "Three", "3", member_in_family))

df <- df %>% mutate(member_in_family = temp_member_in_family$member_in_family)

temp_member_in_family_fixed <- df %>% select(member_in_family) %>% mutate_if(is.character, as.numeric)

df <- df %>% mutate(member_in_family = temp_member_in_family_fixed$member_in_family)

# replacing "Yeso", "1", "0" to "Yes" or "No" based on the values - 'following_company_page' column

df <- df %>% mutate(following_company_page = case_when(following_company_page %in% c("Yeso", "1") ~ "Yes", following_company_page %in% c("0") ~ "No", TRUE ~ following_company_page))


# replacing "0" with "No" - 'working_flag' column

df <- df %>% mutate(working_flag = case_when(working_flag %in% c("0") ~ "No", TRUE ~ working_flag))

df <- df %>% mutate(travelling_network_rating = case_when(travelling_network_rating %in% c(10) ~ 5, TRUE ~ travelling_network_rating))

df
```


After fixing - unique values

```{r}

unique(df$Taken_product)

unique(df$preferred_device)

unique(df$member_in_family)

unique(df$preferred_location_type)

unique(df$following_company_page)

unique(df$working_flag)

unique(df$travelling_network_rating)

unique(df$Adult_flag)
```


# Report


##### Identify and list unique values in the 'Taken_product' and 'preferred_location_type' columns.

```{r}
unique(df$Taken_product)

unique(df$preferred_location_type)
```

##### Distribution of 'Taken_product'

```{r}
ggplot(data= df, aes(x= Taken_product, fill = Taken_product)) + geom_bar() + labs(title = "Distribution of Taken_product")
```


##### What is the distribution of preferred devices among users? Is there a dominant device type?

```{r}
ggplot(data = df, aes(x = device_category, fill = device_category)) +
  geom_histogram(binwidth = 1, color = "black", alpha = 0.7, stat = "count") + labs(title = "Distribution of preferred devices")
```


##### Investigate the distribution of preferred location types. Are there specific location types that users prefer more than others?

```{r}
summary_preferred_location_type <- df %>% group_by(location_type = preferred_location_type) %>% summarise(count = n())
summary_preferred_location_type <- summary_preferred_location_type %>% arrange(desc(count))

ggplot(data = summary_preferred_location_type, aes(y = location_type, x= count)) +
  geom_col(fill = "green", color = "black") + labs(title = "Distribution of preferred location types")
```


##### Explore the distribution of the number of family members traveling with users.

```{r}
ggplot(data = df, aes(x = member_in_family)) +
  geom_histogram(binwidth = 1, fill = "yellow", color = "black", alpha = 0.7, stat = "count")
```


##### Investigate user engagement trends based on the weeks since the last outstation check-in. Are there specific weeks when users are more active?

```{r}
ggplot(data = df, aes(x = week_since_last_outstation_checkin)) +
  geom_histogram(binwidth = 1, fill = "brown", color = "black",  alpha = 0.7, stat = "count") + labs(title = "Week the users are most active")
```


##### Create a scatter plot to visualize the relationship between the number of likes given and received on outstation check-ins.

```{r}
ggplot(data = df, aes(x= total_likes_on_outstation_checkin_given, y= total_likes_on_outofstation_checkin_received)) + geom_point() + labs(title = "Total likes on outstation checkin given vs Total likes on outofstation checkin received")
```


##### What is the distribution of 'travelling_network_rating'? Are most users satisfied with their traveling network?

```{r}
summary_travelling_network_rating <- df %>% group_by(travelling_network_ratings = travelling_network_rating) %>% summarise(rating_count = n(), .groups = "drop")
summary_travelling_network_rating$fac_tnr <- factor(summary_travelling_network_rating$travelling_network_ratings)

summary_travelling_network_rating

ggplot(data = summary_travelling_network_rating, aes(x= fac_tnr, y= rating_count)) + geom_col(fill = "purple", color = "black") + labs(x= "travelling_network_rating", title = "Distribution of travelling_network_rating")

```


##### Explore the distribution of 'Adult_flag.'

```{r}
ggplot(data = df, aes(x= Adult_flag, fill = factor(Adult_flag))) + geom_bar() + labs(title = "Distribution Of Adult Flag")

```


##### How is the daily average minutes spending distributed among users? Are there any significant outliers?

```{r}
ggplot(df, aes(x = "", y = Daily_Avg_mins_spend_on_traveling_page)) +
  geom_boxplot(fill = "orange", color = "black") +
  labs(title = "Distribution of Daily Average Minutes Spending",
       x = "",
       y = "Daily Average Minutes Spending")
```


##### Explore the distribution of 'following_company_page.'

```{r}
fcp_count <- df %>% count(following_company_page)

ggplot(fcp_count, aes(x = "", y= n, fill = factor(following_company_page))) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  labs(title = "Distribution of following_company_page",
       fill = "following_company_page") +
  theme_minimal()
```

##### Correlation Matrix

```{r fig.height=10, fig.width=15}
corr <- df %>% select_if(is.numeric)

correlation_matrix <- cor(corr)

library(corrplot)

corrplot(correlation_matrix, method = "color", col = colorRampPalette(c("blue", "white", "brown"))(50), 
         tl.col = "black")
```

